{\bf \huge Wikiplia}:\\ The Free Programming Language\\ That Anyone Can Edit

### 2007-03-19 trunk/wikiplia/paper/wikiplia.tex
cxpoint

Revision control is accessed through the class of imperative {\tt cvs}
judgments. We assume a single global repository, which maps {\em keys}
(strings) to lists of {\em revisions}. A revision is a monotonically
increasing and unique {\em revision number} (integer) paired with an
XML document. The judgment ${\tt cvs\ commit}\ s\ X = i$ creates a new
revision with revision number $i$ and data $X$ and inserts it under
the key $s$. The judgment ${\tt cvs\ checkout}\ s = X$ fetches the most
recent revision for the key $s$, the document $X$ (if no such key
exists, then the document is invalid). The judgment ${\tt cvs\ 
checkout\ -\!r}\ i\ s = X$ does the same, but for the specific
revision number $i$ (if no such revision exists, the document is
invalid). Finally, ${\tt cvs\ log}\ s = \vec{X}$ fetches all of the
revision numbers for the key $s$, as a series of integers $\vec{X}$.

@@

\subsection{Implementation}
% SML: miserable non-free language

@@

@@

% All popular modern languages are defined via a definitional
% interpreter\wcite{JavaScript}\wcite{Objective Caml}\wcite{Perl} with
% accompanying O'Reilly ``animal'' book.

>>>>

Revision control is accessed through the class of imperative {\tt cvs}
judgments. We assume a single global repository, which maps {\em keys}
(strings) to lists of {\em revisions}. A revision is a monotonically
increasing and unique {\em revision number} (integer) paired with an
XML document. The judgment ${\tt cvs\ commit}\ s\ X = i$ creates a new
revision with revision number $i$ and data $X$ and inserts it under
the key $s$. The judgment ${\tt cvs\ checkout}\ s = X$ fetches the
most recent revision for the key $s$,\z\wcite{Dynamic scope} the
document $X$ (if no such key exists, then the document is invalid).
The judgment ${\tt cvs\ checkout\ -\!r}\ i\ s = X$ does the same, but
for the specific revision number $i$\wcite{Static scope} (if no such
revision exists, the document is invalid). Finally, ${\tt cvs\ log}\ s
= \vec{X}$ fetches all of the revision numbers for the key $s$, as a
series of integers $\vec{X}$.

@@

@@

% XXX main emergency revert

@@

We have reached the end of our journey. But the journey is not
complete! We conclude with a discussion of future plans and unrelated
work, and then conclude with another paragraph.

\subsection{Future Work}

Though Wikipedia in its current form is a usable general-purpose
programming language, work remains to be done for it to reach its full
potential. For one, it needs a vibrant community of contentious and
hubristic editors hiding behind anonymous IP addresses boldly
asserting half-baked syntactic extensions or enforcing superficial
style preferences, gritting their teeth while typing and clicking
white knuckled in a kind of road rage\wcite{List of rages} created by
the dehumanizing semantic markup by which they are forced to
communicate.

We also seek to improve the languages. The language {\tt w} needs many
more features to speed development: the parenthesis-based XESP syntax
should eventually be replaced by a pleasant concrete syntax, if we can
get around to it before too much code is written in XESP.

\subsection{Unrelated Work}

All popular modern languages are defined via a definitional
interpreter\wcite{JavaScript}$^,$\wcite{Objective
Caml}$^,$\wcite{Perl} with accompanying O'Reilly ``animal''
book.\z\wcite{O'Reilly Media} The work on Wikiplia is unrelated: We
have no animal mascot\wcite{ORLY owl} and the languages are described
by a tower of source-to-source translations on top of a universally
parseable semantic document in XML\wcite{Category:ML programming
language family} form.

The author doesn't think much of musicals,\z\wcite{Musical theatre} to
be perfectly honest, so those are basically a no-go. He also feels
that the metric system\wcite{Metric system} and time zones\wcite{Time
zone} are pretty overrated. Ketchup on eggs is gross, but not quite as
gross as foie gras\wcite{Foie gras}, which more or less has the word
``gross'' in its name so duh.\z\wcite{Duh}

\subsection{Another Paragraph}

We have described Wikiplia, the free programming language that anyone
can edit. Unlike other programming languages, it supports a variety of
freedoms (...) and is explicitly scalable to new freedoms. ...
